archivo de trabajo

### 2021-04-26 final/script.Rmd
Update script.Rmd

```{r}
library(readxl)
library(readr)
library(stargazer)
library(dplyr)
library(ggplot2)
censo<-read.csv("censo.csv")#censo es el nombre de la base de datos que bajan de aqui https://www.inegi.org.mx/contenidos/programas/ccpv/iter/zip/iter2020/iter_nalcsv20.zip
planea_15<-read_xlsx("PLANEA_2015.xlsx")
planea_19<-read_xlsx("PLANEA_2019.xlsx")

>>>>

```{r}
library(readxl)
library(readr)
library(stargazer)
library(dplyr)
library(ggplot2)
library(kableExtra)
censo<-read.csv("censo.csv")#censo es el nombre de la base de datos que bajan de aqui https://www.inegi.org.mx/contenidos/programas/ccpv/iter/zip/iter2020/iter_nalcsv20.zip
planea_15<-read_xlsx("PLANEA_2015.xlsx")
planea_19<-read_xlsx("PLANEA_2019.xlsx")
